---
title: "Presentation"
author: "Water Management Project Group"
date: "2023-06-16"
output: html_document
---
#Drip Irrigation adoption in Kenya Irrigation schemes
#Inroduction
Why that Decision- ?
Due to Climate change effects especially the increased events of drought conditions in Kenya, there is a need for proper management and utilization of water resources. Surface irrigation system comprises the biggest percentage in Kenya Irrigation Schemes thus drawing a lot of water from the landscape and negative effect cosharing entities. Therefore we want the government of Kenya to buy into the idea of Drip Irrigation as a sustainable water management approach in the various Irrigation Schemes.

Decision Makers- 
Government of Kenya will be the Decision Makers who also do stakeholder analysis.


#The Project`s Stakeholders 
 The individual/group who has interests/can affect/ is affected by the decision.

After brainstorming and with the help of the STRATEGIC PLAN (2019-2023) by National Irrigation Authority, decided to work on 14 stakeholders.
For each of them, defined : 
      -Roles
      -Major one
      -Rated : 
              -Capital availability
              -Influence
              -Expertise

In the purpose of analyse it and define most important stakeholders and the decision maker
Plot #capital availability, #expertise,  #influence.
```{r}
library(ggplot2)
library(ggrepel)
library(ggthemes)
library(readxl)

stakeholder<-Stakeholder_Management_data <- read.csv("C:/Users/oyiey/OneDrive/Dokumente/UniBonn SS2023/DecisionAnalysis/Dripprojectdata.csv") 
                                                       col_types = c("text", "text", "text", 
                                                                     "numeric", "numeric", "numeric", 
                                                                     "numeric", "numeric")

print(Stakeholder_Management_data)

ggplot(data = stakeholder, aes(x = Expertise, 
                               y = Capital_Availability, 
                               label = Stakeholders, 
                               color = Influence))+  
  geom_point() +
  xlab("Expertise") +
  
  #label names of stakeholders and expand space to show full names
  scale_x_continuous(labels = paste(seq(0, 5, by = 1)), 
                     breaks = seq(0, 5, by = 1), 
                     limits = c(0, 5),
                     expand = c(0, 1)) +
  scale_y_continuous(labels = paste(seq(0, 5, by = 1)), 
                     breaks = seq(0, 5, by = 1), 
                     limits = c(0, 5),
                     expand = c(0, 1)) +
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm")) +
  theme(legend.position = "none") +
  
  # Create line to categorize stakeholders
  geom_hline(yintercept=2.5, color="white", size=2) +
  geom_vline(xintercept=2.5, color="white", size=2) +
  
  # Show all names of overlapped values
  geom_text_repel(box.padding = 0.3, max.overlaps = Inf, size = 3) +
  annotate("text", label = "Potential core experts",
           x = 4.5, y = 3.5, size = 5, color = "grey48") +
  annotate("text", label = "Resource persons",
           x = 4.5, y = 0.25, size = 5, color = "grey48")

```

Government, NGO, irrigation authority = most important (as expected) 
BUT stakeholders with the strongest influence aren’t the best experts and don’t have the biggest available capital (ministry, etc.)





# Conceptual model

Developing this framework opt to include at least most of all the uncertainties, benefits and negative consequences likely to be encountered.
We looked at both short term and long term benefits and general cost for the project.
Government always looks at the social economic value and the viability of the project before making decision to adopt and allocate resources.

## Slide with R Output

```{r}
library(imager)
Conceptual_model <- load.image("C:/Users/oyiey/Downloads/conceptual_model.jpg")
plot(Conceptual_model)

```

## What next
We hope to come up with estimate data that will give value to the uncertainties linked to our project using McSimulation. 
Building the model with Plot of the impact pathway and calibration of the data will consequentially take place.
                   
                   
                   #THANK YOU


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
